
\documentclass[10pt]{amsart}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{multicol}
\usepackage{verbatim}

\textwidth = 6.5 in
\textheight = 9 in
\oddsidemargin = 0.0 in
\evensidemargin = 0.0 in
\topmargin = 0.0 in
\headheight = 0.0 in
\headsep = 0.0 in
\parskip = 0.2in
\parindent = 0.0in

\newtheorem{theorem}{Theorem}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}{Definition}

\newenvironment{packed_enum}{
\begin{enumerate}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
}{\end{enumerate}}

\newenvironment{packed_item}{
\begin{itemize}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
}{\end{itemize}}


\begin{document}
\pagestyle{empty}

\begin{center}
{\bf Class by Class} - Math 393 - Abstract Algebra I - Spring 2019
\end{center}

%%%%%%%%%%%%%%
{\bf Week 1 - Class 1}: Course Introduction\\
%%%%%%%%%%%%%%

(5 minutes) introduction, make sure people know what course it is and what the prerequisites are, advise them to avoid common pitfalls, goals for this course

(15 min)Break up into groups, and have them introduce themselves, read syllabus, generate 4 questions as a group. I then answer them.

(15 min)  Answer the question what do you need to do to be successful in this course?  They share answers, and I show them what students do, then talk about working in small groups and doing the homework.

(15 min)  Have them read the making mistakes page, and talk about that in relation to the homework.

(15 min) Regroup students and have them introduce themselves and and work on the triomino problem.
 
 (Last 5 minutes) Assignments:  Go to CI Learn site, look over sample homework writeup, look at the math writing guide, and the homework grading.  Start work on the introductory assignment memo.

%%%%%%%%%%%%%%
{\bf Week 1 - Class 2}: Section 3.1 Integer Equivalence Classes and Symmetries\\
%%%%%%%%%%%%%%

%%%%%%%%%%%%%%
{\bf Week 2 - Class 1}: Section 3.2 Definitions and Examples\\
%%%%%%%%%%%%%%

%%%%%%%%%%%%%%
{\bf Week 2 - Class 2}: Section 3.3 Subgroups\\
%%%%%%%%%%%%%%
	
%%%%%%%%%%%%%%
{\bf Week 3 - Class 1}: Section 4.1 Cyclic Subgroups\\
%%%%%%%%%%%%%%


%%%%%%%%%%%%%%
{\bf Week 3 - Class 2}: Section 4.2 Multiplicative Group of Complex Numbers\\
%%%%%%%%%%%%%%

%%%%%%%%%%%%%%
{\bf Week 4 - Class 1}: Section 4.3 The Method of Repeated Squares\\
%%%%%%%%%%%%%%

%%%%%%%%%%%%%%
{\bf Week 4 - Class 2}: Section 5.1 Definitions and Notation\\
%%%%%%%%%%%%%%

%%%%%%%%%%%%%%
{\bf Week 5 - Class 1}: Section 5.2 Dihedral Groups\\
%%%%%%%%%%%%%%

%%%%%%%%%%%%%%
{\bf Week 5 - Class 2}: Section 6.1 Cosets \\
%%%%%%%%%%%%%%

%%%%%%%%%%%%%%
{\bf Week 6 - Class 1}: Section 6.2 Lagrange's Theorem\\	
%%%%%%%%%%%%%%

%%%%%%%%%%%%%%
{\bf Week 6 - Class 2}: Section 6.3 Fermat's and Euler's Theorems\\
%%%%%%%%%%%%%%

%%%%%%%%%%%%%%
{\bf Week 7 - Class 1}:  Section 9.1 Definition and Examples\\
%%%%%%%%%%%%%%

%%%%%%%%%%%%%%
{\bf Week 7 - Class 2}: Section 9.2 Direct Products  \\
%%%%%%%%%%%%%%

%%%%%%%%%%%%%%
{\bf Week 8 - Class 1}: Midterm
%%%%%%%%%%%%%%

%%%%%%%%%%%%%%
{\bf Week 8 - Class 2}: Flexible
%%%%%%%%%%%%%%

%%%%%%%%%%%%%%
{\bf Week 9 - Class 1}: Section 10.1 Factor Groups and Normal Subgroups \\
%%%%%%%%%%%%%%

%%%%%%%%%%%%%%
{\bf Week 9 - Class 2}: Section 10.2 The Simplicity of the Alternating Group\\
%%%%%%%%%%%%%%

%%%%%%%%%%%%%%
{\bf Week 10 - Class 1}: Section 11.1 Group Homomorphisms\\
%%%%%%%%%%%%%%

%%%%%%%%%%%%%%
{\bf Week 10 - Class 2}: Section 11.2 The Isomorphism Theorems \\
%%%%%%%%%%%%%%

%%%%%%%%%%%%%%
{\bf Week 10 - Class 2}: Section 16.1 Rings\\
%%%%%%%%%%%%%%

%%%%%%%%%%%%%%
{\bf Week 11 - Class 1}:  Section 16.2 Integral Domains and Fields  \\
%%%%%%%%%%%%%%

%%%%%%%%%%%%%%
{\bf Week 11 - Class 2}: Section 16.3 Ring Homomorphisms and Ideals\\
%%%%%%%%%%%%%%

%%%%%%%%%%%%%%
{\bf Week 12 - Class 1}:  Section 16.4 Maximal and Prime Ideals\\
%%%%%%%%%%%%%%

%%%%%%%%%%%%%%
{\bf Week 12 - Class 2}: 16.5 An Application to Software Design (CRT)\\
%%%%%%%%%%%%%%

%%%%%%%%%%%%%%
{\bf Week 13 - Class 1}: 
%%%%%%%%%%%%%%

%%%%%%%%%%%%%%
{\bf Week 13 - Class 2}: 
%%%%%%%%%%%%%%

%%%%%%%%%%%%%%
{\bf Week 14 - Class 1}: 
%%%%%%%%%%%%%%

%%%%%%%%%%%%%%
{\bf Week 14 - Class 2}:
%%%%%%%%%%%%%%

%%%%%%%%%%%%%%
{\bf Week 15 - Class 1}: Special Topic or Catch up
%%%%%%%%%%%%%%
Chapter 17?

%%%%%%%%%%%%%%
{\bf Week 15 - Class 2}: Special Topic or Catch up
%%%%%%%%%%%%%%
Chapter 17?


\end{document}

